Supplementary Material for 'The complex network of trophic interactions in

### 2024-01-11 MS_ToSubmit/SupMaterial.Rmd
Fix table format

---
title: "Supplementary Material for 'The complex network of trophic interactions in
  a subAntarctic oceanic Marine Protected Area'"
author:
  - Tomás I. Marina
  - Irene R. Schloss
  - Gustavo A. Lovrich
  - Claudia C. Boy
  - Daniel O. Bruno  
  - Fabiana L. Capitanio
  - Sergio M. Delpiani
  - Juan Martín Díaz de Astarloa
  - Cintia Fraysse
  - Virginia A. García Alonso
  - Andrea Raya Rey
  - Laura Schejter
  - Mariela L. Spinelli
  - Marcos Tatián
  - Diego Urteaga
  - Luciana Riccialdelli
bibliography: AMPBancoBurdwood.bib
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

@@

```{r ref_plot, echo=FALSE, fig.cap="Summary of references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}

@@

```{r tableS1, echo=FALSE, results='asis'}

# Load packages
library(knitr)
library(dplyr)
library(kableExtra)
library(pander)

@@

# Discard low resolution interactions
int_good_res <- int_raw %>% 
  filter(!str_detect(Prey, "\\*$")) %>% 
  filter(!str_detect(Predator, "\\*$")) %>% 
  mutate(Prey = case_when(Prey == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ "Other")) %>%
  dplyr::select(Prey, Predator, Reference, Reference_link) %>% 
  distinct(Prey, Predator, .keep_all = TRUE)

# Table 1. List of interactions
knitr::kable(int_good_res %>% arrange(., (Predator)), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem. Alphabetically ordered by predator.") %>% 
  column_spec(1:3, width="2cm") %>% 
  column_spec(4, width="14cm") %>% 
  kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4) %>% 
  landscape()

# pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Reference_link = paste('\\tiny', Reference_link)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right"),
#              caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")

@@

```{r tableS2, echo=FALSE, results='asis'}

# Load packages
library(knitr)
library(dplyr)
library(kableExtra)
library(stringr)

@@

# Table 2. List of species
knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Taxonomy","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Areas Namuncurá - Banco Burdwood I and II ecosystem. Alphabetically ordered by species.") %>%
  column_spec(1:3, width="2cm") %>%
  column_spec(4, width="3cm") %>% 
  column_spec(5:6, width="5cm") %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4) %>% 
  landscape()

@@

```{r tableS3, echo=FALSE}

@@

# Table 2. List of species
knitr::kable(spp_total %>% 
               mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon",
                                          TRUE ~ TopRole)) %>% 
               dplyr::select(TrophicSpecies, FunctionalGroup, TotalDegree, NumPrey, NumPred, Between, Close, TL, meanTrophicSimil, TopRole) %>% 
               arrange(., desc(TotalDegree)) %>% 
               mutate(across(where(is.numeric), round, 4),
                      FunctionalGroup = case_when(TrophicSpecies == "Brachiopoda_spp" ~ "Brachiopoda",
                                                  TrophicSpecies == "Campylaspis_spp" ~ "Cumacea",
                                                  TRUE ~ FunctionalGroup)), 
             format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem. Ordered by degree (total number of interactions). Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).") %>%
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4.5)

@@

@@

```{r toprole_graph, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Circle diameter is relative to the number of interactions."}

>>>>

---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
  word_document: default
# classoption: landscape
bibliography: AMPBancoBurdwood.bib
csl: "elsevier-harvard2.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{amsmath}
- \usepackage{pdflscape,booktabs}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

# Supplementary Material for 'The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area'

@@

```{r ref_plot, echo=FALSE, message=FALSE, fig.cap="Summary of references used to build the network of trophic (predator-prey) interactions for the MPAN-BB ecosystem."}

@@

\newpage
\blandscape

```{r tableS1, echo=FALSE, message=FALSE, results='asis'}

# Load packages
require(tidyverse)
require(knitr)
require(dplyr)
require(kableExtra)
require(pander)

@@

# Discard low resolution interactions
int_good_res <- int_raw %>% 
  dplyr::filter(!str_detect(Prey, "\\*$")) %>% 
  dplyr::filter(!str_detect(Predator, "\\*$")) %>% 
  mutate(Prey = case_when(Prey == "Brachiopoda_spp" ~ "Brachiopoda", TRUE ~ Prey)) %>%
  dplyr::select(Prey, Predator, Reference, Reference_link) %>% 
  distinct(Prey, Predator, .keep_all = TRUE)

# Table 1. List of interactions
# landscape(knitr::kable(int_good_res %>% arrange(., (Predator), booktabs = TRUE, format = "latex", longtable = T, col.names = c("Prey","Predator","Reference", "Link"), caption = "List of predator-prey (trophic) interactions for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem. Alphabetically ordered by predator.") %>%
#              column_spec(1:3, width="2cm") %>% 
#              column_spec(4, width="14cm") %>% 
#              kable_styling(latex_options = c("hold_position","repeat_header"), font_size = 4))

pandoc.table(int_good_res %>% arrange(., (Predator)) %>% mutate(Prey = paste('\\tiny', Prey), Predator = paste('\\tiny', Predator), Reference = paste('\\tiny', Reference), Reference_link = paste('\\tiny', Reference_link)) %>% rename("Link"="Reference_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right"),
             caption = "List of predator-prey (trophic) interactions used to build the network for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem (MPAN-BB).")

@@

```{r tableS2, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load packages
# library(knitr)
# library(dplyr)
# library(kableExtra)
# library(stringr)

@@

# Table 2. List of species
# knitr::kable(sp_list, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Taxonomy","Group","Reference","Link","Observation"), caption = "List of species for the food web of the Marine Protected Areas Namuncurá - Banco Burdwood I and II ecosystem. Alphabetically ordered by species.") %>%
#   column_spec(1:3, width="2cm") %>%
#   column_spec(4, width="3cm") %>% 
#   column_spec(5:6, width="5cm") %>% 
#   kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 4) %>% 
#   landscape()

pandoc.table(sp_list %>% arrange(., (Species)) %>% mutate(Species = paste('\\tiny', Species), TaxLevel = paste('\\tiny', TaxLevel), FunctionalGroup = paste('\\tiny', FunctionalGroup), Reference = paste('\\tiny', Reference), Reference_pres_link = paste('\\tiny', Reference_pres_link), Observation = paste('\\tiny', Observation)) %>% rename("Taxonomy"="TaxLevel", "Group"="FunctionalGroup", "Link"="Reference_pres_link"), style="multiline", split.tables = Inf, justify = c("left","left","left","right","right","left"),
             caption = "List of species for the food web of the Marine Protected Areas Namuncurá - Banco Burdwood I and II ecosystem. Alphabetically ordered by species.")

@@

```{r tableS3, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

@@

# Table 3. List of species
tbl_3 <- spp_total %>% 
  mutate(TopRole = case_when(TopRole == "hubcon" ~ "netcon", TRUE ~ TopRole)) %>% 
  dplyr::select(TrophicSpecies, FunctionalGroup, TotalDegree, NumPrey, NumPred, Between, Close, TL, meanTrophicSimil, TopRole) %>% 
  arrange(., desc(TotalDegree)) %>% 
  mutate(across(where(is.numeric), round, 4),
         FunctionalGroup = case_when(TrophicSpecies == "Brachiopoda_spp" ~ "Brachiopoda",
                                     TrophicSpecies == "Campylaspis_spp" ~ "Cumacea",
                                     TRUE ~ FunctionalGroup))
# tbl_31 <- kableExtra::kbl(tbl_3, format = "latex", booktabs = TRUE, linesep = "", longtable = TRUE, col.names = c("Species","Group","Degree","NumPrey","NumPred","Between","Close","TL","TS","TR"), align = "llcccccccc", caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem. Ordered by degree (total number of interactions). Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).")
# tbl_32 <- kableExtra::kable_styling(tbl_31, latex_options = c("hold_position", "repeat_header"), font_size = 4.5)

pandoc.table(tbl_3 %>% arrange(., (TotalDegree)) %>% rename("Species"="TrophicSpecies", "Group"="FunctionalGroup", "Degree"="TotalDegree", "TS"="meanTrophicSimil", "TR"="TopRole"), style="multiline", split.tables = Inf, justify = c("left","left","center","left","left","left","left","left","left","left"),
             caption = "Species-level properties for the food web of the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem. Ordered by degree (total number of interactions). Between: betweenness; Close: closeness; TL: trophic level; TS: trophic similarity; TR: topological role (netcon = network connector, modcon = module connector, modhub = module hub, modspe = module specialist).")

@@

\elandscape
\newpage

@@

```{r toprole_graph, echo=FALSE, message=FALSE, warning=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Circle diameter is relative to the number of interactions."}
